Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-29 WSSSPE4_report/WSSSPE4_report.tex
spelling

A later question looked at the common practices from software engineering that the scientific community should be using.
The discussion that followed picked up on the key elements of basic sustainable practice: version control, documentation and ensuring that communities are active and engaged.
When asked whether there was resistance from the research community to adopting these practices, few negative experiences were reported.
From the panel's point of view, it would appear that the problem in getting researchers to employ sustainable practicies lies more in getting the message out to researchers, rather than selling them on the benefits.

>>>>

A later question looked at the common practices from software engineering that the scientific community should be using.
The discussion that followed picked up on the key elements of basic sustainable practice: version control, documentation and ensuring that communities are active and engaged.
When asked whether there was resistance from the research community to adopting these practices, few negative experiences were reported.
From the panel's point of view, it would appear that the problem in getting researchers to employ sustainable practices lies more in getting the message out to researchers, rather than selling them on the benefits.
